---
title: "6/7-8 Functions"
author: "Skylar A. Gay"
date: "6/8/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(dplyr)
library(ggplot2)
library(corrplot)
library(cluster) 
library(fpc)
library(devtools)
library(ggpubr)
library(C50)
library(tidyverse)
library(cowplot)

ggplotsmooth <- function(df){
  ggplot(df, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) + 
    geom_point() + 
    geom_smooth()
}
ggplotline <- function(df){
  ggplot(data = df, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) + 
    geom_smooth(aes(linetype = Species), size = 1, se = FALSE) + 
    geom_point(aes(shape = Species), size = 3) + 
    scale_shape_manual(values = c(16, 17, 18)) + 
    scale_color_manual(values = c("purple",
                                  "black",
                                  "orange")) + 
    scale_linetype_manual(values = c("solid",
                                     "dashed",
                                     "twodash"))
}
fctvert <- function(df){ #vertical
  ggplot(data = df, aes(x = Sepal.Length, y = Sepal.Width)) + 
    geom_point(size = 3) + 
    geom_smooth(size = 1, se = FALSE) + 
    facet_wrap(~ Species)
}
fcthor <- function(df){
  ggplot(data = df, aes(x = Sepal.Length, y = Sepal.Width)) + 
    geom_point(size = 3) + 
    geom_smooth(size = 1, se = FALSE) + 
    facet_grid(rows = vars(Species))
}
gpplot <- function(df){
  ggplot(df, aes(carat, price)) + 
    geom_point(alpha = 0.05) + 
    scale_y_continuous(trans = "log") + 
    scale_x_continuous(trans = "log")
}
ghplot <- function(df){
  ggplot(df, aes(price)) + 
    geom_histogram()
}
gbplot <- function(df){
  ggplot(df, aes(x = cut)) + 
    geom_bar()
}
gbplotcy <- function(df){
  ggplot(df, aes(cut, fill = clarity)) + 
    geom_bar()
}
gcplot <- function(df){
  ggplot(data.frame(x = c(1, 1, 2, 2, 3, 3), 
                    y = c(40, 60, 30, 70, 20, 80), 
                    z = c("A","B","A","B", "A", "B")), aes(x, y, fill = z)) + 
    geom_col()
}
gbarplot <- function(df){
  ggplot(df, aes(cut, fill = clarity)) + 
    geom_bar(position = "dodge")
}
gjplotcy <- function(df){
  ggplot(df, aes(cut, clarity)) + 
    geom_jitter(alpha = 0.05)
}
gjplot <- function(df){
  ggplot(df, aes(Sepal.Length, Sepal.Width, color = Species)) + 
    geom_jitter() + 
    scale_color_manual(values = c("black",
                                  "green",
                                  "magenta"))
}
gbxplot <- function(df){
  ggplot(df, aes(cut, price)) + 
    geom_boxplot()
}
gptplot <- function(df){
  ggplot(df, aes(Sepal.Length, Sepal.Width, color = Species)) + 
    geom_point() + 
    scale_color_manual(values = c("black",
                                  "green",
                                  "magenta")) +
    theme_bw()
}
glplot <- function(df){
  ggplot(data.frame(x = 1:10, 
                    y = 61:70), aes(x, y)) + 
    geom_line() + 
    background_grid()
}
glncol <- function(df){
  ggplot(df, aes(x = Year)) + 
  geom_line(aes(y = Winter), color = "black") + 
  geom_line(aes(y = Spring), color = "green") + 
  geom_line(aes(y = Summer), color = "magenta") + 
  geom_line(aes(y = Fall), color = "cornflowerblue")
}
ute <- function(df){
  unite(
  (separate
   (df, 
     Results, 
     c("FirstRace", "SecondRace", "ThirdRace"), 
     sep = "-")), 
  TotalTime, 
  TotalMinutes, 
  TotalSeconds, 
  sep = ":")
}
mttdbl <-  function(df){
  mutate(dblcol = AvgTemp * 2)
}
mttdblsqr <- function(df){
  LongTemps %>%
  mutate(TwiceTemp = AvgTemp * 2,
         TwiceSquaredTemp = TwiceTemp^2,
         YearSeason = paste(Year, Season))
}
avg <- function(df){
  mean(df$col)
}
testcor <- function(df){
  cor.test(iris$Sepal.Length, iris$Sepal.Width)
}
fltrcol <- function(df){
  df[df$Sepal.Length > 7.5, ]
}
fltrtp <- function(df){
  df %>%
  filter(Species == "setosa")
}
fltrtpcol <- function(df){
  df %>%
  filter(Species == "setosa" & Sepal.Length == 5.1 & Sepal.Width == 3.3)
}
mttmn <- function(df){
iris %>%
  select(c(Sepal.Length, Species)) %>%
  group_by(Species) %>%
  mutate(SLDistanceFromGroupMean = Sepal.Length - mean(Sepal.Length)) %>%
  ungroup() %>%
  mutate(SLDistanceFromTotalMean = Sepal.Length - mean(Sepal.Length))
}